Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-20 analysis/paper/paper.Rmd
clarify dropping molecular focus as an article criteria used in evaluation

Due to differences in evaluators' interpretations (Fig ZZZZ) of whether or not an article had a molecular focus or not, this scoring criteria was not used in the overall evaluation.

>>>>

Due to differences in evaluators' interpretations (Fig ZZZZ) of whether or not an article had a molecular focus or not, this scoring criteria was dropped from the analysis and is not reported here.
